A parametric system for generating contour parallel toolpaths with adaptive extrusion width

### 2019-08-24 0_main.tex
limitations
redo abstract

	\usepackage{listings} % for listing C++ code instead of pseudocode
	\lstset{ 
      breaklines=true,                 % sets automatic line breaking
    }

@@

\begin{abstract}
3D printing techniques such as Fused Deposition Modeling (FDM) have enabled the fabrication of complex geometry quickly and cheaply. 
FDM builds up objects by depositing material along toolpaths which lie in horizontal layers.
The outlines of each layer are filled using contour-following toolpaths approximately the size of the printing nozzle.
Filling the outlines with extruded material densely is important for fabricating parts with high stiffness and dimensional accuracy.
An accurate dense filling is especially important for thin parts such as casings for electronics, blowmolding prototypes, (architectural) models, and microstructures.

A naive strategy for densely filling the outlines of a layer determines the toolpaths by performing inward offsets from the outline shape of a constant width.
In the center of the outline shapes this naive strategy can result in underfill regions and overfill regions as wide as the nozzle size.
Some previous literature solves these overfill and underfill problems by locally extruding a small amount of material less or more.
However, such methods inevitably generate extrusion toolpaths with widths wildly differing from the nozzle size, which are difficult to manufacture.
We propose a framework which allows to define beading strategies which distribute the overfill and underfill required in each region over nearby toolpaths, so that we considerably reduce the amount of extrusion toolpaths with extreme widths.

Our method determines the number of extrusion beads at each location, then it generates the beads from the center of the outline shape outward and finally connects all bead together to form extrusion toolpaths.
We determine the middle of the shape by applying a significance measure to the skeleton of the outline polygon, use the beading strategy to determine the optimal number of beads in those middle regions and derive the toolpath locations as distances from the middle parts of the skeleton from the beading strategy.
Because the skeletal structure decomposes the outline domain into simple cells, the toolpaths can be generated by drawing straight line segments along each cell.

Our framework is shown to be able to emulate several methods discussed in related literature and it enables a wide range of other beading strategies.
We show that we can define a strategy which reduces the amount of overfill and underfill compared to previous literature and we show that the extrusion widths have less deviation from the nozzle size.
We show that our implementation exhibits computation times in the same order of magnitude as the naive method.
\end{abstract}

>>>>

	\usepackage{listings} % for listing C++ code instead of pseudocode
	\lstset{ 
      breaklines=true,                 % sets automatic line breaking
      basicstyle=\ttfamily,
      mathescape
    }

@@

\begin{abstract}
3D printing techniques such as Fused Deposition Modeling (FDM) have enabled the fabrication of complex geometry quickly and cheaply. 
FDM builds up objects by depositing material along toolpaths which lie in horizontal layers.
The outlines of each layer are filled using contour-following toolpaths approximately the size of the printing nozzle.
Filling the outlines with extruded material densely is important for fabricating parts with high stiffness.
An accurate dense filling is especially important for thin parts such as casings for electronics, blowmolding prototypes, (architectural) models, and microstructures.

A naive strategy for densely filling the outlines of a layer determines the toolpaths by performing inward offsets from the outline shape of a constant width.
In the center of the outline shapes this naive strategy can result in underfill regions and overfill regions as wide as the nozzle size.
Existing techniques address these over- and underfill issues by locally extruding a small amount of material less or more in those regions.
However, such methods inevitably generate extrusion toolpaths with widths wildly differing from the nozzle size, which are difficult to manufacture accurately.
We propose a framework which allows to define beading strategies which distribute the overfill and underfill required in each region over nearby toolpaths, so that we considerably reduce the amount of extrusion toolpaths with extreme widths.

Based on a skeletonization of the 2D outline shape of a single layer we generate a 3D surface mesh, the union of cones.
By slicing the surface at regular heights we obtain contour parallel toolpaths which cover the 2D area of a single layer.
The heights of the 3D mesh are first altered:
the heights at central ridges in the 3D surface are flattened to be parallel with the slicing planes in order to prevent over- and underfill
and the heights in other regions are modified in such a way that the deviation from the nominal extrusion width is distributed over several beads around the center of the shape.

Our framework is shown to be able to emulate several methods discussed in related literature and it enables a wide range of other beading strategies.
We show that we can define a strategy which reduces the amount of overfill and underfill compared to previous literature and we show that the extrusion widths have less deviation from the nozzle size.
We show that our open source implementation exhibits computation times in the same order of magnitude as the naive method.
\end{abstract}
